A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Finished the proof that QCiso(G) = H^1(k,G^*). Added a remark after the lemma on global sections.
Explained that the lemma on global sections is the genesis of the
hypothesis on G for the sheaf-function dictionary for G.

%\begin{proposition}\label{tensor}
The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
with duals given by applying the functor 
$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in
$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.

@@

 \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
  for all $x,y \in G(\bFq)$, such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
    && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
    \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
   \end{tikzcd}
  \]
  commutes, for all $x,y,z\in G(\bFq)$; and

 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
    && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
    && \gcs{L}_x \otimes\gcs{L}_y
   \end{tikzcd}
  \]
  commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}
Under this equivalence, a morphism $\alpha : \cs{L} \to \cs{L'}$ of quasicharacter sheaves on $G$ is given by 
\begin{enumerate}
 \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
  of linear transformations (of one-dimensional $\EE$-vector spaces),
  as $x$ runs over $G(\bFq)$, such that
  \[
   \begin{tikzcd}[column sep=40]
    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes \alpha_y} & \gcs{L'}_x \otimes \gcs{L'}_y
   \end{tikzcd}
  \]
  both commute.
\end{enumerate}

\begin{lemma}\label{lemma:section}
 If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying
 \begin{equation}\label{section}
  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
 \end{equation}
\end{lemma}

\begin{proof}
  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
  \[
  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
  \]
  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
  We will define a section $s$ by choosing values on these generators and extending to all
  of $G(\bFq)$ through \eqref{section}.

  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
  to the multiplication map $\EE \otimes \EE \to \EE$.
  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
  then forces $s(0) = 1$.

@@

These sections will allow us to construct the isomorphism in the following proposition.

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
  \qquad \text{given by}\qquad
  [\cs{L}] \mapsto [\tau_\cs{L}],
  \]
  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
  \[
  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
  \]
\end{proposition}

\begin{proof}
  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  Using Lemma~\ref{lemma:section}, we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G(\bFq)}$ and
  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of section.

@@

  Although we used a global section $s$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
  For each $x \in G(\bFq)$ there is a unique scalar
  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
  \begin{equation}\label{cohomologous}
    \obj \QC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
  Let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $\delta: G(\bFq) \to \EEx$
  by $\varphi_x(s(x)) = \delta(x) s'(x)$.
  By the second part of condition~\ref{cs.3},
  $\delta(x+y) = \delta(x)\delta(y)$, so $\delta \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\delta \cdot \delta^{-1})$,
  so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
  \begin{equation}\label{pich1}
    \QCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
  \end{equation}

  It only remains to show that \eqref{pich1} is a group
  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves.
  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
\Clifton{I'm working on this.}
\end{proof}

>>>>

%\begin{proposition}\label{tensor}
The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
$\cs{L} \otimes_{\EE}\cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
with duals given by applying the functor 
$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
is not a tensor category in the sense of \cite{deligne:02a}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\QC(G)$ puts a group
structure on the set $\QCiso{G}$ of isomorphism classes in
$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.

@@

 \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y}$,
  for all $x,y \in G(\bFq)$, such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
    && \gcs{L}_{x+y}\otimes_{\EE}\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
    \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y+z} \arrow{rr}{\id \otimes_{\EE}\mu_{y,z}}
    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes_{\EE}\gcs{L}_{z}
   \end{tikzcd}
  \]
  commutes, for all $x,y,z\in G(\bFq)$; and

 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
    && \gcs{L}_{\Frob{\Fq}(x)}\otimes_{\EE}\gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
    && \gcs{L}_x \otimes\gcs{L}_y
   \end{tikzcd}
  \]
  commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}
Under this equivalence, a morphism $\alpha : \cs{L} \to \cs{L'}$ of quasicharacter sheaves on $G$ is given by 
\begin{enumerate}
 \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
  of linear transformations (of one-dimensional $\EE$-vector spaces),
  as $x$ runs over $G(\bFq)$, such that
  \[
   \begin{tikzcd}[column sep=40]
    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes_{\EE}\alpha_y} & \gcs{L'}_x \otimes_{\EE}\gcs{L'}_y
   \end{tikzcd}
  \]
  both commute.
\end{enumerate}

\begin{lemma}\label{lemma:section}
 If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying
 \begin{equation}\label{section}
  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes_{\EE}s(y).
 \end{equation}
\end{lemma}

\begin{proof}
  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
  \[
  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
  \]
  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
  We will define a section $s$ satisfying \eqref{section} by choosing values on these generators and extending to all
  of $G(\bFq)$ through \eqref{section}.

  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
  to the multiplication map $\EE \otimes_{\EE}\EE \to \EE$.
  The condition $\mu_{0,0}(s(0)) = s(0) \otimes_{\EE}s(0)$ together with the non-triviality of $s$
  then forces $s(0) = 1$.

@@

The main result of Part~\ref{part1} of this paper, 
the sheaf-function dictionary for $G$ Theorem~\ref{thm:snake}, has a hypothesis: 
the smooth commutative group scheme locally of finite type must have the 
property that the geometric component group of $G$ is finitely generated as a group. 
The genesis of that hypothesis is Lemma~\ref{lemma:section},
as we use this hypothesis to show the existence of global sections of $\gcs{L}$ satisfying \eqref{section} for $\mu$.
Remarkably, Lemma~\ref{lemma:section} is the only crux for this hypothesis;
that is, if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
and if each quasicharacter sheaf on the etale group scheme $\pi_0(G)$ admits a global section 
satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$,
so there is a sheaf-function dictionary for $G$.

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
  \qquad \text{given by}\qquad
  \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}],
  \]
  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
  \[
  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
  \]
\end{proposition}

\begin{proof}
  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  
  Using Lemma~\ref{lemma:section}, 
  we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G}$ and
  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.

@@

  Although we used a global section $s$ in the definition of
  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
  choice. To see why, let $s_1$ and $s_2$ be two global sections of
  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
  For each $x \in G(\bFq)$ there is a unique scalar
  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
  defined by $\tau_0(\Frob{\Fq}) = \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
  \begin{equation}\label{cohomologous}
    \obj \QC(G) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
  \end{equation}
  is independent of the choice of global sections made above.

  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
  Let $\alpha : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
  according to Lemma~\ref{lemma:sec}.
    Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
  by $\alpha_x(s(x)) = a(x) s'(x)$.
  By the second part of condition~\ref{cs.3},
  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
  so $\tau$ and $\tau'$ are cohomologous. This shows that
  \begin{equation}\label{pich1}
    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}]
  \end{equation}
  is well-defined.

 The paragraph above also shows that \eqref{pich1} is injective. 
 Suppose $[\tau_\cs{L}] = [\tau_\cs{L'}]$.
 Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\cs{L}$ (resp. $\tau_\cs{L'}$);
 recall that $s$ (resp. $s'$) is compatible with $\mu$ (resp $\mu'$) 
 in the sense of Lemma~\ref{lemma:section}.
 Since $[\tau_\cs{L}] = [\tau_\cs{L'}]$, 
 it follows that $\tau_\cs{L}$ and $\tau_{\cs{L'}}$ are cohomologous, 
  so there is some $a\in G(\Fq)^*$ such that 
  $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$. 
  Define $\alpha : \cs{L}\to \cs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
  it is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
  and that $\alpha^{-1} : \cs{L'}\to \cs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
  is its inverse. Thus, $\cs{L} \iso \cs{L'}$ in $\QC(G)$. 
  This shows that \eqref{pich1} is injective.

  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves on $G$.
  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes_{\EE}s'$ is a global section for
  $\cs{L} \otimes_{\EE}\cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes_{\EE}\cs{L}'$ imply that
  $\tau_{\cs{L} \otimes_{\EE}\cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.

 Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
 For each $x\in G(\bFq)$, set $\gcs{L}_x = \EE$.
 Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes_{\EE} \gcs{L}_y$ by
 $\mu_{x,y}(1) = 1\otimes_{\EE}1$, for $x,y\in G(\bFq)$; 
 clearly, $\mu$ satisfies condition~\ref{cs.1}.
 Define $\phi_x : \gcs{L}_{\Frob{\Fq}} \to \gcs{L}_x$ by $\phi_x(1) = \tau(\Frob{\Fq})(x)$,
 for each $x\in G(\bFq)$. 
 Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
 In this way we have built a quasicharacter sheaf $\cs{L} = (\gcs{L},\mu,\phi)$ 
 from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\cs{L}_{/\text{iso}}$
 under \eqref{pich1} is the class $[\tau]$ in $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
 This shows that \eqref{pich1} is surjective, 
 and completes the proof that it is an isomorphism of groups.
\end{proof}
